%-------------------------
% Resume in Latex
% Author : Harshibar
% Based off of: https://github.com/jakeryang/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
% only for pdflatex
% \input{glyphtounicode}

% fontawesome
\usepackage{fontawesome5}

% fixed width
\usepackage[scale=0.90,lf]{FiraMono}

% light-grey
\definecolor{light-grey}{gray}{0.83}
\definecolor{dark-grey}{gray}{0.3}
\definecolor{text-grey}{gray}{.08}

\DeclareRobustCommand{\ebseries}{\fontseries{eb}\selectfont}
\DeclareTextFontCommand{\texteb}{\ebseries}

% custom underline
\usepackage{contour}
\usepackage[normalem]{ulem}
\renewcommand{\ULdepth}{1.8pt}
\contourlength{0.8pt}
\newcommand{\myuline}[1]{%
  \uline{\phantom{#1}}%
  \llap{\contour{white}{#1}}%
}

% custom font: helvetica-style
\usepackage{tgheros}
\renewcommand*\familydefault{\sfdefault}
\usepackage[T1]{fontenc}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{0in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% sans serif sections
\titleformat {\section}{
    \bfseries \vspace{2pt} \raggedright \large
}{}{0em}{}[\color{light-grey} {\titlerule[2pt]} \vspace{-4pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-1pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & {\color{dark-grey}\small #2}\vspace{1pt}\\
      \textit{#3} & {\color{dark-grey} \small #4}\\
    \end{tabular*}\vspace{-4pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
      #1 & {\color{dark-grey}\small #2} \\
    \end{tabular*}\vspace{-4pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{0pt}}

\color{text-grey}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge ISHAN VAIBHAV} \\ \vspace{5pt}

    \small
    \faPhone* \texttt{7061101978} $|$
    \faEnvelope \ \href{mailto:ishanvaibhav12@gmail.com}{ishanvaibhav12@gmail.com} $|$
    \faLinkedin \ \href{https://www.linkedin.com/in/ishan-vaibhav-9a38952a9}{LinkedIn} $|$
    \faGithub \ \href{https://github.com/ishanvaibhav}{GitHub} $|$
    \faCode \ \href{https://leetcode.com/u/ishan_26/}{LeetCode} $|$
    \faChartBar \ \href{https://www.kaggle.com/ishanvaibhav}{Kaggle}

    \\ \vspace{-3pt}
\end{center}

%-----------EXPERIENCE-----------
\section{EXPERIENCE}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Teachnook}{Oct. 2023 -- Nov. 2023}
      {Artificial Intelligence Trainee}{Bangalore, India}
      \resumeItemListStart
        \resumeItem{Developed a machine learning model for predicting \textbf{chronic kidney disease} using healthcare datasets.}
        \resumeItem{Performed \textbf{data preprocessing, feature engineering, and exploratory data analysis (EDA)} using Pandas and NumPy.}
        \resumeItem{Trained and evaluated classification models using \textbf{Scikit-learn}, achieving strong performance in accuracy, precision, and F1-score metrics.}
        \resumeItem{Identified key medical indicators that significantly influence kidney disease prediction outcomes.}
        \resumeItem{Project Repository: \href{https://github.com/Shwetraj1/ckd-ai-assistant}{\myuline{CKD AI Assistant}}}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{PROJECTS}
    \resumeSubHeadingListStart

      \resumeProjectHeading
          {\textbf{Global Market Layoffs Analysis} $|$ SQL, Power BI}{2024}
          \resumeItemListStart
            \resumeItem{Cleaned and transformed a dataset of \textbf{2000+ global layoff records} using SQL with CTEs, joins, and window functions.}
            \resumeItem{Handled missing values, standardized company and industry fields, and removed duplicate entries to improve data quality.}
            \resumeItem{Built an interactive Power BI dashboard to analyze layoff trends by company, industry, funding stage, and geographic region.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Nephro AI -- Kidney Disease Prediction System} $|$ Python, Machine Learning}{2023}
          \resumeItemListStart
            \resumeItem{Developed a machine learning model to predict \textbf{chronic kidney disease} using healthcare datasets.}
            \resumeItem{Performed exploratory data analysis, data preprocessing, and feature engineering using Pandas and NumPy.}
            \resumeItem{Trained classification models using Scikit-learn and evaluated them with accuracy, precision, and F1-score.}
            \resumeItem{GitHub: \href{https://github.com/Shwetraj1/ckd-ai-assistant}{\myuline{CKD AI Assistant Repository}}}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{AeroSense -- Predictive Maintenance System} $|$ Python, Machine Learning}{2024}
          \resumeItemListStart
            \resumeItem{Built a predictive maintenance system using time-series sensor data to identify patterns that signal upcoming equipment failures.}
            \resumeItem{Applied preprocessing techniques and \textbf{SMOTE} to address class imbalance in rare failure events and improve model learning.}
            \resumeItem{Trained ensemble models including Random Forest and XGBoost to detect potential system failures and support proactive maintenance decisions.}
          \resumeItemListEnd

    \resumeSubHeadingListEnd

\section{EDUCATION}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Uttarakhand Technical University}{2023 -- 2027}
      {B.Tech in Computer Science and Engineering (Data Science Specialization)}{Dehradun, India}
        \resumeItemListStart
            \resumeItem{\textbf{CGPA}: 7.4 / 10}
            \resumeItem{\textbf{Relevant Coursework}: Data Structures, DBMS, Statistics, Machine Learning, Artificial Intelligence, Big Data Analytics}
        \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{SKILLS}
 \begin{itemize}[leftmargin=0in, label={}]
    \small{\item{
     \textbf{Languages}: Python, SQL, Java, C++ \\
     \textbf{Data Analysis}: Pandas, NumPy, Excel, Power BI, Tableau \\
     \textbf{Machine Learning}: Scikit-learn, TensorFlow, Feature Engineering, Model Evaluation \\
     \textbf{Tools}: Git, GitHub, Jupyter Notebook, Google Colab, Oracle Cloud
    }}
 \end{itemize}

\section{CERTIFICATIONS}
\resumeItemListStart
\resumeItem{\textbf{Oracle Cloud Infrastructure 2025 Certified Data Science Professional}}
\resumeItem{\textbf{Oracle Analytics Cloud 2025 Certified Professional}}
\resumeItem{\textbf{Oracle Cloud Infrastructure 2025 Certified AI Foundations Associate}}
\resumeItem{Artificial Intelligence -- Teachnook}
\resumeItemListEnd

\section{ACHIEVEMENTS}
\resumeItemListStart
\resumeItem{Project selected at \textbf{state level} in the OpenAI \& NxtWave Hackathon for developing an innovative AI-based solution.}
\resumeItem{Active problem solver on \href{https://leetcode.com/u/ishan_26/}{\myuline{LeetCode}} focusing on algorithms and data structures.}
\resumeItem{Maintains technical projects and machine learning implementations on \href{https://github.com/ishanvaibhav}{\myuline{GitHub}}.}
\resumeItemListEnd

%-------------------------------------------
\end{document}
